\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{acl2017}
\usepackage{url}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{float}

\floatstyle{boxed}
\restylefloat{figure}

\aclfinalcopy

\title{SLING: A framework for frame semantic parsing}

\author{
Michael Ringgaard \\ Google Inc. \\ {\tt ringgaard@google.com} \\\And
Rahul Gupta \\ Google Inc. \\ {\tt grahul@google.com} \\
}

\date{}

\begin{document}
\maketitle

\begin{abstract}
This technical report describes SLING, which is a framework for building
parsers for annotating text with semantic frames.
The parser is a general transition-based frame semantic parser using
bi-directional LSTMs for input encoding and a Transition Based Recurrent
Unit (TBRU) for output decoding.
It is a jointly trained model using only the text tokens as input and the
transition system has been designed to output frame graphs directly without
any intervening symbolic representation.
The SLING framework includes an efficient and scalable frame store
implementation as well as a neural network JIT compiler for fast parsing at
runtime.
The SLING framework is implemented in C++ and it is available for download
on GitHub.
\end{abstract}

\section{Introduction}

Recent advances in machines learning has enabled us to use deep learning to
train recurrent multi-level neural network classifiers. This has allowed us to
reconsider how to best design and implement systems for natural language
understanding (NLU).

Traditionally, natural language processing (NLP) systems have used a cascade of
NLP modules for syntatic and semantic annotation of text.
These systems typically first do part-of-speech (POS) tagging, followed by
constituency or dependency parsing for syntactic analysis.
Using the POS tags and parse trees as feature inputs, you could then do other
NLP tasks like mention chunking, entity type tagging, coreference resolution,
semantic role labeling (SRL), etc.

Pipelined systems often use a simple 1-best feed forward strategy \cite{finkel2006}
where they greedily take the best output of each stage and pass it on to the
next stage.
While it is simple to build such an architecture, errors can accumulate
throughout the pipeline making it much harder for the system to perform
correctly, e.g. F1 on SRL drops by more than 10\% when going from gold to
automatic parse trees \cite{toutanova2005}.

Often, applications do not need the intermediate annotations produced
by the lower levels in the NLP stack, so it would be preferable if these systems
could be trained jointly to optimize an objective based on the output
annotations needed for a particular application.

Classic NLP systems are also often trained using linear classifiers.
Because of the simplicity of these, very complex and elaborate feature
extraction with many different types of features as well as many kinds
of combinations of these features are often required for good accuracy.
With deep learning you can use embeddings, multiple layers, and recurrent
network connections instead, and this will often remove the need for complex
feature designs. The internal learned representations in the hidden layers of
the models can be used instead of the hand-crafted intermediate representations
in pipelined systems.

To address these problems, we have made the SLING parser. It is a
transition-based parser that outputs frame graphs directly without any
intervening symbolic representation (see Section~\ref{sec:ts}). Transition-based
parsing is often associated with dependency parsing, but we have designed a
specialized transition system that outputs frame graphs instead of dependency
trees.

We use a recurrent feed-forward unit for predicting the actions in the
transition sequence, where the hidden activations from precting each transition
step is feed back into the subsequent steps.
We use a bidirectional LSTM for encoding the input, where we have both a
left-to-right and a right-to-left LSTM. This neural network architecture
has been implemented using DRAGNN \cite{dragnn} and Tensorflow \cite{tensorflow}.

We have made the SLING parsing framework available as open source and the code
for the parser described in this paper can be found on GitHub.\footnote{\url{https://github.com/google/sling}}

In Section~\ref{sec:framesem} we introduce \emph{frame semantics}, which is the
underlying linguistic theory, as well as the SLING frame store, which is our
C++ framework for repesenting, storing, inspecting, manipulating, and
transporting semantic frames compactly and efficiently.
Section~\ref{sec:ts} describes the transition system used for producing the
frame graphs and Section~\ref{sec:features} describes the features used by the parser.

\section{Frame semantics}
\label{sec:framesem}

While frames in SLING are not tied to any particular frame semantic theory or
knowledge ontology, they are inspired by \emph{frame semantics}, which is a
theory of linguistic meaning developed by Charles Fillmore \cite{fillmore1982}.
Frame semantics connects linguistic semantics to encyclopedic knowledge and the
central idea is that understanding the meaning of a word requires access to all
the essential knowledge that relates to that word. A word \emph{evokes} a frame
repesenting the specific concept it refers to.

A semantic frame is a set of facts that specify "characteristic
features, attributes, and functions of a denotatum, and its characteristic
interactions with things necessarily or typically associated with it." \cite{alan2001}.
A semantic frame can also be vieved as a coherent structure of related concepts
that are related such that knowledge of all of them is required to have
complete knowledge of any one.

Frame semantics is not only for individual concepts, but can be generalized
to phrases, entities, constructions, and other larger and more complex linguistic
and ontological units. Semantic frames can be also used in information modeling
for constructing knowledge bases of world knowledge and common sense, and frame
semantics can also form the basis for reasoning about metaphors, metonymy,
actions, perspective, etc.

At a more technical level, a SLING frame consists of a list of slots, where each
slot has a name (role) and a value. The slot values can be literals like numbers
and strings, or links to other frames. The frames essentially form a graph where
the frames are the (typed) nodes and the slots are the labeled edges. A frame
graph can also be viewed as a feature structure \cite{carpenter2005} and
unification can be used for induction of new frames from existing frames.
Sometimes it is also useful to use frames for representing more basic data
structures like a C struct with fields, a JSON object, or a record in a
database.

SLING frames live inside a \emph{frame store}. A store is a container that
tracks the all the frames that have been allocated in the store, and serves as a
memory allocation arena for the allocated frames. When making a new frame, you
specify the store that the frame should be allocated in. The frame will live in
this store until its store is deleted or the frame is garbage collected because
there are no references to it.\footnote{See the \href{https://github.com/google/sling/blob/master/frame/README.md}{SLING Guide}
for a detailed description of the SLING frame store implementation.}

Documents are also represented using frames, where the document frame has slots
for the document text, the tokens, and the mention phrases and the frames they
evoke. See Figure~\ref{fig:slingdoc} for an example.

\begin{figure*}[t]
  \begin{verbatim}
  :/s/document
  /s/document/text: "John hit the ball"
  /s/document/tokens: [
    {/s/token/text: "John" /s/token/start: 0  /s/token/length: 4},
    {/s/token/text: "hit"  /s/token/start: 5  /s/token/length: 3},
    {/s/token/text: "the"  /s/token/start: 9  /s/token/length: 3},
    {/s/token/text: "ball" /s/token/start: 13 /s/token/length: 4}
  ]
  /s/document/mention: {
    :/s/phrase /s/phrase/begin: 0
    /s/phrase/evokes: {=#1 :/s/person }
  }
  /s/document/mention: {
    :/s/phrase /s/phrase/begin: 1
    /s/phrase/evokes: {
      :/pb/hit-01
      /pb/arg0: #1
      /pb/arg1: #2
    }
  }
  /s/document/mention: {
    :/s/phrase /s/phrase/begin: 3
    /s/phrase/evokes: {=#2 :/s/consumer_good }
  }
\end{verbatim}
  \caption{The text "John hit the ball" in SLING frame notation. The document
  itself is represented by a frame that has the text, an array of tokens and
  the mentions that evoke frames. There are three frames: a person frame (John),
  a consumer good frame (bat) and a hit-01 frame. The hit frame has the person
  frame as the agent (arg0) and the ball frame as the object (arg1).}
  \label{fig:slingdoc}
\end{figure*}

\section{Transition system}
\label{sec:ts}

In the parsing litteratur, \emph{transition systems} have been
used to construct dependency parse trees from a sequence of state-action pairs
$(s_i,a_i)$. A transition system takes a state $s_i$ and an action $a_i$ and
constructs a new state $s_{i+1}$. This allows you to build a tree structure by
predicting a sequence of actions. For example, the \emph{arc-standard}
transition system \cite{nivre2006} uses {\bf SHIFT}, {\bf LEFT-ARC(label)}, and
{\bf RIGHT-ARC(label)} actions to construct a dependency parse tree from a
sequence of these actions.

We are using the same core idea to construct a frame graph where frames can be
evoked by phrases in the input. Instead of using a stack, we have an
\emph{attention buffer}, which keeps track of the most salient frames in the
discourse. The front of the attention buffer serves as the short-term memory of
the parser and the parser actions operate on these frames. The actions in the
transition system both builds up the frame graph as well as maintaining the
attention buffer.

\begin{itemize}
  \item {\bf SHIFT} -- Skips the next input token. Only valid when not at the
        end of the input buffer.
  \item {\bf STOP} -- Signals that we have reach the end of the parse. This is
        only valid when at the end of the input buffer. Multiple STOP actions
        can be added to the transition sequence, e.g. to make all sequences in a
        beam have the same length.
  \item {\bf EVOKE(type, n)} -- Evokes frame of with type {\bf type} from
        the next {\bf n} tokens in the input. The new frame will become the
        center of attention.
  \item {\bf REFER(frame, n)} -- Makes a new mention of the next {\bf n} tokens
        in the input evoking an existing frame in the attention buffer. This
        frame will become the new center of attention.
  \item {\bf CONNECT(source, role, target)} -- Adds slot to {\bf source} frame
        in the attention buffer with name {\bf role} and value {\bf target}
        where {\bf target} is an existing frame in the attention buffer. The
        {\bf source} frame become the new center of attention.
  \item {\bf ASSIGN(frame, role, value)} -- Adds slot to {\bf source} frame in
        the attention buffer  with name {\bf role} and value {\bf value} and
        moves the frame to the center of attention.
  \item {\bf EMBED(target, role, type)} -- Creates a new frame with
        type {\bf type} and add a slot to it with name {\bf role} and value
        {\bf target} where {\bf target} is an existing frame in the attention
        buffer. The new frame becomes the new center of attention.
  \item {\bf ELABORATE(source, role, type)} -- Creates a new frame with type
        {\bf type} and adds a slot to an existing frame {\bf source} in the
        attention buffer with {\bf role} set to the new frame. The new frame
        becomes the new center of attention.
\end{itemize}

This transition system can generate any connected frame graph, where the frames
are either directly on indirectly evoked by mention phrases in the text. A frame
can be evoked by multiple mentions and the graph can have cycles.

Multiple transition sequences can generate the same frame annotations, but we
have implemented an oracle sequence generator that takes a sentence and converts
it to a canonical transition sequence in a similar way to how this is done
for transition-based dependency parsing \cite{nivre2006}, e.g. the sentence
"John hit the ball" will generate the following transition sequence:
\begin{verbatim}
  EVOKE(/s/person, 1)
  SHIFT
  EVOKE(/s/hit-01, 1)
  CONNECT(0, /pb/arg0, 1)
  SHIFT
  SHIFT
  EVOKE(/s/consumer_good, 1)
  CONNECT(1, /pb/arg1, 0)
\end{verbatim}

\section{Features}
\label{sec:features}

The LSTMs only uses lexical features based on the current input word:

\begin{itemize}
  \item The current word is mapped through pre-trained word embeddings
  \cite{mikolov2013} for all the words known in the vocabulary from the
  training data.
  \item The prefixes and suffixes of the current input word. Currently only
  prefixes up to three characters are used.
  \item Word shape features based on the characters in the current input word:
  hyphenation, capitalization, punctuation, quotes, and digits.
\end{itemize}

The feed-forward unit takes the hidden activation from the LSTMs as well as the
activations in the hidden layer of the feed-forward unit from the previous steps
as input features and uses these to compute the following input features:

\begin{itemize}
  \item The hidden activations from the left-to-right and right-to-left LSTMs
  for the current token in the parser state.
  \item The attention feature looks at the top-5 frames in the attention buffer
  and tracks the phrases in the text that evoked them. The activations from the
  left-to-right and right-to-left LSTMs for the end token in these phrase are
  added as input features. These serve as the lexical representation of the top
  frames in the attention buffer.
  \item The transition steps which evoked or re-evoked the top-5 frames in the
  attention buffer are used as the semantic context representation for these
  frames. The hidden activations in the feed-forward unit at these steps are
  input as features to the current step in the feed-forward unit.
  \item The history feature uses the hidden activations in the feed-forward
  unit from the previous five step as feature inputs to the current step.
  \item The roles features extract the role edges between the top-5 frames in
  the attention buffer. These are triples of the form $(s_i, r_i, t_i)$ meaining
  that the frame at position $s_i$ in the attention buffer has a role $r_i$ with
  the frame at position $t_i$ in the attention buffer as its value. Back-off
  features are added for the source roles $(s_i,r_i)$, target role $(r_i, t_i)$,
  and unlabeled roles $(s_i,t_i)$.
\end{itemize}

\section{Parser runtime}

Myelin is a neural network JIT compiler...

At training time, we use Tensorflow for computing and updating the neural
network.

\section{OntoNotes corpus}

Descibe how the OntoNotes-based training and testing corpus was constructed...

\section{Evaluation}

An annotated document consists of a number of connected frames and as well as
phrases, i.e. token spans, evoking these frames. We evaluate the accuracy of the
annotations by comparing the generated frames with the gold standard frame
annotations from the evaluation corpus.

The documents are matched by constructing a virtual graph where the document
is the start node. The document node is then connected to the spans and the
spans are connected to the frames that the spans evoke. This graph is then
extended by following the frame-to-frame links from the roles. Accuracy is
computed by aligning the golden and predicted graphs and computing precision,
recall, and F1. The accuracy is computed for spans, frames, types, roles, and
labels.

\section{Furture work}

% Cascading action classifier to speed up computations of logits... TBD

% Knowledge-based inference... TBD

\section{Acknowledgments}

\bibliography{sling}
\bibliographystyle{acl_natbib}

\end{document}

